---
title: "Zia's data"
author: "Kathleen"
date: "2023-02-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
mydata <- read.csv(file="zia data.csv")
mydata$Scorpion_ID <- as.factor(mydata$Scorpion_ID)

```

#   Analysis of NumProbes
```{r}
boxplot(NumProbes~Scorpion_ID,data=mydata)
```
  
The scorpion_ID with a lower temperature looks to have a higher rate in the Number of Probes compared to the higher temperature of the scorpion_ID where it consists a lower Number of Probes. 
  
Numerical Data
```{r}
favstats(NumProbes~Scorpion_ID,data=mydata)
```
    
Results with a higher temperature carries a lower median of 6.0 compared to the lower temperature where it's medium consists of 17.5. Taking a closer look at the average amount of probes for the higher temperature carries the number 6.5 while the average amount of probes located in the lower temperature is 23.5.
  
Inferential Data
```{r}
t.test(NumProbes~Scorpion_ID,data=mydata)
```
In conclusion, the difference between the two recordings of data differentiated by temperature carry a large difference. Where the lower temperature requires a larger amount of probing compared to scorpions in a higher temperature. This statement can be proven through the three data charts showing the differences.

#   Analysis of TimeSting

```{r}
boxplot(TimeSting~Scorpion_ID,data=mydata)
```
  
Looking at the provided data, it appears that the scorpion took more time in trying to sting when presented at a lower temperature. When presented at a higher temperature, it took less time for the stings to occur.
  
Numerical Data
```{r}
favstats(TimeSting~Scorpion_ID,data=mydata)
```
  
Looking at the presented data, scorpions stuck in a higher temperature have a median of 7.2 and a mean of 11.03792. Comparing this to the other scorpion stuck in a lower temperature where the median consists of 25.2 and a mean of 34.42917.
  
  Inferential Data
```{r}
t.test(TimeSting~Scorpion_ID,data=mydata,conf.level=.99)
```
  
During a 90% confidence level, the difference between the scorpions within different temperatures. Now comparing the data to having the confidence level raised to 99%, the amount of confidence intervals change in a small amount.


